Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-07 highlights.tex
Changes in the highlights

\begin{itemize}
\item A study on methods to overlap the search space in distributed multi-objective evolutionary algorithms is carried out
\item A new adaptive overlapping mechanism is presented
\item Different combinations of number of islands, genome sizes, benchmarks and methods are used
\item Different quality metrics have been compared
\item Results are validated in a real system
\item All overlapping schemes outperform the baseline, being the adaptive method the one that obtains the best performance
\end{itemize}
\end{document}

>>>>

\begin{itemize}
\item ------------------------------------------------------------------------------------
\item A study on methods to overlap the search space in distributed MOEAs is carried out  
\item A new automatic overlapping mechanism is presented
\item Results are validated in a real system, using different quality metrics
\item Relation between the number of islands and chromosome length is a relevant factor
\item Best results are obtained when increasing the dimensionality and overlapping size
%\item A study on methods to overlap the search space in distributed multi-objective evolutionary algorithms is carried out
%\item A new adaptive overlapping mechanism is presented
%\item Different combinations of number of islands, chromosome sizes, benchmarks and methods are used
%\item Different quality metrics have been compared
%\item Results are validated in a real system
%\item Results show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is a relevant factor to determine the most efficient alternative to distribute the decision variables
%\item The higher the dimensionality and the overlapping, the greater the benefit of distribution in a large number of islands
\end{itemize}
\end{document}
